Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-01 neurips-20/cvx-flats.tex
Adding the t example

>>>>

\section{Omitted examples}
\paragraph{A weather example:}
Consider the following scenario where someone is deciding how to dress for their bike ride.\jessiet{Someone just went to the bike shop...}
They want to wear a rain jacket if it rains, but don't want to have to carry it around if it doesn't rain.
Moreover, they might want their base layer to be appropriate for the heat.
Consider the three outcomes $\Y = \{$sunny, cloudy, rainy$\}$, and we suppose we want to bring a jacket if $Pr[ y= $rain | weather conditions] $ \geq 3/5$.
Moreover, we want to wear a short sleeved shirt if $Pr[y= $sunny | weather conditions] $ \geq$ $Pr[y= $cloudy | weather conditions], and long-sleeved otherwise.

We can now model this problem by a property with the reports $\R = \{$rain jacket and short-sleeve base layer (rj,ss), rain jacket and long-sleeve base layer (rj,ls), no rain jacket, short-sleeve (no rj,ss), no rain jacket, long-sleeve (no rj,ls)$\}$, where $\Gamma(p)$ is shown in Figure~\ref{fig:t-example}.
However, we do not have a target loss for this problem, so constructing a consistent surrogate for this problem is ill-defined without Definition~\ref{def:consistent-prop} unless one takes the time to try to reverse engineer a target loss, which faces the problem of scale as properties become more intricate.

Our bounds from Theorem~\ref{thm:cvx-flats} on the distribution $p = (1/5, 3/5, 1/5)$ suggest that the convex elicitation complexity $\eliccvx(\Gamma) \geq 3 - 0 -1 = 2$, since there is no way to draw a line through $p$ while staying in just one level set on the simplex.
This bound is the same as those given by feasible subspace dimension, but we cannot definitely say anything about convex calibration dimension since we do not have a target loss.
\jessie{Do we want to construct a convex surrogate for this?  Not super clear how...}

This example, although rather silly, can also extend to other decision-tree-like properties that do not have an explicit or easily constructed target loss.

\begin{figure}
	\centering
	\includegraphics[width=0.4\linewidth]{tikz/t-example.pdf}
	\caption{Our example on how to dress for a bike ride.}
	\label{fig:t-example}
\end{figure}
